### 2019-04-24 manuscript.tex
Changes made
Updated scripts to be more legible
Also added to manuscript

\begin{titlepage}
	\centering
	%\includegraphics[width = number\textwidth]{image title}\par\vspace{1cm}}
	%this could be used to add the Aberdeen logo?
	%{\scshape\Large The University of Aberdeen \par}
	%\vspace{1cm}
	{\huge\bfseries Asymetry and the Absence of Patterns Do Not Encourage Optimal Decisions.\par}
	\vspace{1cm}
	Warren \textsc{James}, \par
	Dr.~Amelia \textsc{Hunt},\par
	and\par
	Dr.~Alasdair \textsc{Clarke}
	\vfill
\end{titlepage}

@@

\paragraph{} Some theories assume that people generally aim to make decisions that offer the greatest expected utility \citep{mongin1997expected}. However, problems can become intractable as the number of possible outcomes to compare grows \citep[see ][ for a discussion of this]{BOSSAERTS2017917}. Therefore, when thinking of optimal decisions, one must take into account the limitations of the indivdual. This is termed Bounded Rationality \citep{simon1990invariants} and posits that people do make optimal decisions given some limitations.

@@

\paragraph{} This possibility was investigated in \cite{James2017} using the \textit{Throwing Task} with the added measure of what participants understood their ability to be.  The results of this experiment suggested that all participants had a very clear understanding of their own ability. Prompting participants to think about their accuracy on each trial, however, did not appear to make participants better able to solve the problem presented to them. The results of \cite{James2017} appear to suggest either a failing of \textit{Bounded Rationality} in that participants were not considering/using knowledge of their ability to accuractely throw bean bags appropriately, or that they were simply more focused on other aspects of the task that may have caused them to ignore this information. In the four studies presented here, the aim was to investigate what aspects of the task may have interfered with the participants' ability to figure out the optimal strategy.

@@

\subsection*{Probability Matching}
\addcontentsline{toc}{subsection}{Probability Matching}
%This is just a temporary intro to this section that can be edited at any point depening on where it is positioned in the final version
\paragraph{} The first of these factors to be investigated is that of \textit{Probability Matching}. This is often regarded as a suboptimal behaviour as it does not offer the greatest rate of success \citep{Koehler2010}. An eaxmple of this would be if one was tasked with selecting between two options several times in a row. If option A would reward you 80\% of the time, and option B only 20\% of the time. The best course of action is to pick option A every time as this would result in an average success rate of 80\%. Whereas trying to match the probabilities by selecting each option in proportion to its likelihood of success would only yield an average success rate of 68\%.

@@

\paragraph{} As \cite{wolford2004searching} suggest, this search for a pattern may hinder performance in tasks in which there is no true pattern to find. In the context of \cite{clarke2015failure}, this may have interfered with participants using information about their own ablity to make decisions. Instead, they may have been attempting to figure out any patterns that they believed may have been present. %In study 2 of this paper, a bias for one side was included to examine whether participants would begin to make use of this information. The hypothesis was that in a context where each option is equally likely, we should replicate the results of \cite{clarke2015failure}, however, once a bias is added, participants would be more likely to prioritise this target and begin to opt for choosing to attempt one task rather than try to achieve both.

@@

\begin{figure}
	\centering
	\captionsetup{justification=centering}
	\subfloat{\includegraphics[height = 10cm, width = 15cm]{Figures/Experiment_4_prob/exp_vs_opt_bias_lines}}\quad
	\subfloat{\includegraphics[height=10cm,width=15cm]{Figures/Experiment_4_prob/exp_vs_opt_rand_lines}}
	\caption{The different lines represent the predicted accuracy given the particiapnt had employed either the optimal or centre strategy, and their expected accuracy given the fixation locations the participant made in the experiment.}
	\label{fig:Session2-prob-accresults}
\end{figure}

@@

\paragraph{} The results of both \cite{CHAPMAN2010168} and \cite{Hudson2007probmove} suggest that people were trying to give themselves a more evenly distributed chance of success. This suggests that participants preferred more equal odds of success to having a hight chance of success for some (if not 100\%) and the other having a much lower chance of success (if not $\approx$0\%). Also, in \cite{Hudson2007probmove}, we can see how participants demonstrated a reluctance to move entirely towards the most probable location and instead favoured points that allowed for a small chance of success should the unlikely happen.

@@

\paragraph{} To confirm this, a General Linear Mixed Effects model with a binomial link was used. For the model, the small hoop being on the left or right was used a predictor for whether the participant stood either on the left or right of centre. The results of this model were significant suggesting that pariticipants were more likely to stand towards the small hoop than the large one (the model specification can be seen below). This suggests that participants were somewhat aware that their chances would improve slightly should they have stood slightly closer to the smaller hoop. This is in line with the data presented by \cite{CHAPMAN2010168} in that the participants were positioning themselves in such a way that may have given them a more equal chance of success should either target be the target for that trial.

@@

\paragraph{} Upon inspecting Figure \ref{fig:Session2-Hoopsizes-Accuracy}, there is little noticeable difference between the expected accuracy should the participant have decided to stand equidistant from each hoop or in the position that offered the participant more equal chance of success. Additionally, by creating a more tangible situation in which there is a clear reason to priori tise one target over the other, participants generally still do not appear to reach the optimal solution. Participants 10, 11, and 12 are close to achieving optimal accuracy for both the closest and furthest hoops, however, as can be seen in Figure \ref{fig:Session2-Hoopsizes-Accuracy}, they still fall short of reaching optimal accuracy.

@@

\paragraph{} In \textit{Experiment 2}, the intention was to provide participants with a more tangible experience of one of the potential targets being more rewarding than the other. Similar to the results of \cite{CHAPMAN2010168} and \cite{Hudson2007probmove}, the participants in this experiment appeared to demonstrate a gen eral tendency to move towards a position that would offer them a more equal chance of success. This is demonstrated by participants on average standing towards the smaller hoops in this task. However, this change to the paradigm still did not facilitate a better understanding of the task that would lead to an optimal strategy being implemented.

@@

\paragraph{} From visually inspecting Figure \ref{fig:Session2-TwoThrows}, one can see that for the most part, the number of throws had no real effect on where particpants chose to stand. The only participant that appears to show some difference is participant 15 and this is in the oppossite direction to what would have been expected should removing any reason to search for patterns had impeded participants' ability to figure out the optimal strategy.

@@

\paragraph{} Inspecting Figure \ref{fig:Session2-TwoThrows-Accuracy} demonstrates that most participants achieved an accuracy that would be expected had they followed the Centre strategy. The one exception to this is participant 13 who appears to achieve an accuracy close to the optimal strategy. By looking at the participant's standing positions in \ref{fig:Session2-TwoThrows}, this would make sense as they appear to switch at an appropriate point given their own ability to perform in this task. Although they did appear to stand outside the range for some distances, it appears that they were were more likely to stand in a central position for the smallest distances, and towards one of the sides for the larger distances.

@@

\paragraph{} As with any decision to be made, having appropriate incentives for success can be important. \cite{phillips1966conservatism} investigated this idea by tasking participants with estimating whether a bag they had been handed contained predominantly red or blue chips. They were told there were 10 bags in total with $X$ containing predominantly red chips and $10 - X$ containting predominantly blue chips. They were then told that the bags that contained mainly red chips either contained 70\% red chips and 30\% blue, or 60\% red and 40\% blue with the inverse of these being true for the predominantly blue bags. They were then presented with 20 chips from the selected bag and were asked to give an estimate of how likely the bag the chips were drawn from was a majority red or majority blue bag. What they found was that participants estimates were fairly conservative when compared to what would be expected via Bayesian inference. They questioned whether this could be due to a lack of incentive to perform this task more effortfully.

@@

\paragraph{} Another example of a payoff structure altering the behaviour of participants can be seen in \cite{Goodnow1955} in which participants that were rewarded for performance were more likely to employ a more optimal strategy. They tasked participants with making judgements of which event would occur on each trial. The likelihood of each event occuring was set in one of three ways; being equally likely, a 70\% bias in favour of one event, or a 90\% bias in favour of one event occurring. Half the participants were told that the task was one of learning and that they were to uncover some underlying principle, whereas the other half were told that the task was one of gambling in which they were to place a bet on which event was likely to occur on each trial. They found that participants in the gamble condition when there was a 70\% bias were more likely to opt for a \textit{maximising} strategy than those in the problem solving condition. This was also true for the 90\% bias condition, but the effect appeared less pronounced.

\paragraph{} Although these studies do suggest that a financial incentive may have pushed some participants to perform the task in a more optimal way, it did not cause them to perform the tasks perfectly optimally. In a review by \cite{Camerer1999}, it is argued that a financial incentive is not entirely enough to remove all irrational behaviours. This can clearly be seen in \cite{morvan2012human} in which participants receieved a small sum of money for every successful trial. Despite this financial incentive, participants did not appear to behave any differently to those in \cite{clarke2015failure} who did not pay their participants any amount for successful trials.

@@

\subsection*{Preface}
\addcontentsline{toc}{subsection}{Preface}
\paragraph{} As mentioned before, in \textit{Experiment 1}, participants were tasked with tracking a fairly abstract concept of probability. They would have needed to recognise that the location with the highest likelihood of containing the target would reward them with the greatest rate of return in the long term. As such, it is possible that participants did not see the more likely option as being more valuable, but instead would try to make use of this information in another way. \cite{Goodnow1955} demonstrated that when participants were offered a financial incentive for success, they were more likely to make use of a maximising strategy over the less optimal alternative of probability matching. In \textit{Experiment 4}, we attempted to investigate this by intorducing a very clear, external reward for successful performance in the task.

@@

\subsubsection*{Procedure} 
\paragraph{} Participants signed a consent which contained details about the reward schedule and how much they could expect to earm on average. All participants were given £4 as a baseline and were told that they could expect to earn an addtional amount ranging from £0 to £4.80 depending on their performance. They were also told that we expected them to earn between £1.50 and £2.50 on average.

@@

\paragraph{} There were two main changes to the paradigm for this experiment. Firstly, instead of calculating 3 distances, 4 were calculated. Now, the distances at which participants were 90\%, 75\%, 25\%, and 10\% accurate were used. Addtionally, participants were now told they had 50p to split between the two target items in one of two ways. They could either split it equally across both potential targets (25p/25p) or make it an 80/20 split (40p/10p). Participants were asked how they would like to split the money before they made a choice about where to stand. If they opted to make an unequal split, they were asked which hoop they would like to be worth 40p and which 10p. Participants were informed that the target hoop had been predetermined so that each hoop was equally likely to be the target on each trial and that there was no pattern. It was reaffirmed that any money they earned by successfully throwing the bean bag into the target hoop would be given to them upon completing the experiment. Participants would then pick a place to stand, at which point they would be told which hoop was the target for that trial and their standing position was recorded covertly.

@@

\paragraph{} As can be seen in Figure \ref{fig:DecisionPhase_Reward}, participants generally tended towards splitting the monetary value in an Equal fasion. Only four participants opted for en Unequal split most of them time, but no participants followed the truly optimal rule of always splitting the value Unequally which would have given participants a larger rate of return.

@@

\paragraph{} However, these two experiments do offer some insight into information people may be attempting to make use of when performing these sorts of tasks. For example, in \textit{Experiment 1}, participants generally were more likely to prioritise one side over the other when there was a reason to do so. Although they did not quite make use of this information in an optimal way (i.e. by exlcusively fixating the more likely box) as would be expected \citep{koehler2014probability}, there was a difference when compared to a situation in which each option was equally likely. This adds further support to the notion that people are sensitive to this information and will make use of it when making decisions \citep{wolford2004searching,yellott1969probability}. Due to this, it is possible that participants were in fact making an attempt to maximise their rate of success, but were doing so using a suboptimal strategy \citep{Gao2015}.

@@

\subsection*{Confidence}
\addcontentsline{toc}{subsection}{Confidence}
\paragraph{} In general, participants still made suboptimal decisions accross all tasks. This raises the question of whether participants are making their decisions about where to stand with confidence, or whether they recognise when they are doing something that might not be "correct". \cite{SZOLLOSI20171} presented people with a series of questions with the three items from the Cognitive Reflection Task \citep[CRT: ][]{Frederick2005CRT}. These items are designed so that an inuitive, but incorrect, answer will spring to mind. An example of one of these items the bat and ball problem which goes as follows; \textit{"a bat and a ball cost \pounds1.10. The bat costs \pounds1.00 more than the ball. How much does the ball cost?"} The correct answer is 5p, yet many people often state the ball is worth 10p causing the total to be \pounds1.20 \citep{Frederick2005CRT}. In the study by \cite{SZOLLOSI20171}, they gave people many problems like these and also asked participants to give a rating of how confident they were that they had given the correct answer. When tasked with answering the items from the CRT and giving the wrong answer, particiapnts tended to be less confident that they had given the right answer. Additionally, their participants indicated that they had also spent less time trying to figure out the answer to questions they were less confident in. They argued that these coupled together suggest that people recognised that the task was "too difficult" and offered the solution that first came to mind.

\paragraph{} The idea that people may simply give up and offer the first solution that comes to mind is similar to the idea of "satisficing" \citep{simon1990invariants}. This is when someone finds a task too difficult and as such attempts to solve the problem using little effort such as using a strategy that has worked before in other contexts. It's possible that once participants find the tasks in this paper to be too difficult, they gave up and continued to behave in the same way as before. One way to investigate this would be to use a similar paradigm to that employed by \cite{Kiani759}. In their study, they presented monkeys with a large number of moving dots on a screen and they were to report the "global direction" of the dots (i.e. were they mainly moving to the left or the right). For each correct answer, they receieved an amount of juice In some cases this would be easy to estimate as a large proportion of the dots would be moving as a group. However, in some cases, only a small proportion would be moving in one direction with the rest moving at random. In these situations it became more difficult for them to discern the "global direction" of the dots. On random trials they were offered a third option that would offer a certain reward, but this was worth less than if they gave the correct answer. What they found was that the monkeys would use this option when the task was more difficult.

\paragraph{} This idea of confidence could easily be incorporated into the tasks used in this paper in order to investigate whether people may simply be satisfising rather than trying to figure out a solution. Much like in \cite{Kiani759}, a third option could be introduced on random trials that would give a small but certain reward. If participants are able to recognise their own ability to perform but cannot figure out the solution to the task, then what would be observed is that participants would continue to stand more towards the centre, but only opt for the 3rd, lesser value but certain option, when the task became harder. 
%This would enatil that participants would need to have some sort of performance related reward, and although this does not seem to make a difference when comparing the performance of participants with reward \citep{morvan2012human} and without \citep{clarke2015failure}, it does allow for the hypothesis that participants are simply satisfying to be investigated.
%Satisfising is argued to be due to people reaching a certain success threshold and the ceasing to search for alternative strategies that may improve their performance. As such, it would be possible to alter the amount of reward participants would receive if they selected the 3rd option. With a setup like this, it would be possible to investigate whether a lack of confidence in one's capacity to solve this problem results in settling for a relatively low success rate.

%This paragraph is weak... maybe rephrase it a bit or develop the idea a bit more?
%\paragraph{} Additionally, adding a financial incentive for success allows for other potential factors to be investigated. Although in \cite{James2017}, participants were able to give accuracte measures of their own ability, this does not necessarily mean that they would incorporate this information into their decision making. \cite{Goodnow1955} argued that in the context of problem solving, people are more likely to probability match, within a gambling context, people tend to maximise. Within the context of this study, the paradigm could be altered so that participants would have sum of money they would split between each target. For example, they could split the amount equally between each target. If the they were then successful for the selected target, they would receive the amount they had placed on that target. By doing this, participants would now have more reason to consider their odds of success should they desire to gain the largest financial reward. This would make it so that not only would participants be considering their own ability to perform, but it may push them to incorporate this information more effectively into their decision making, rather than possibly treating it as an extra task to be performed concurrently.
%
\subsection*{Certainty}
\addcontentsline{toc}{subsection}{Certainty}
%\paragraph{} Adding in a gambling element may lead participants to consider aspects of the problem that they may not have considered without this extra factor. 
\paragraph{} None of these experiments are able to investigate an intriguing contradiction in \cite{clarke2015failure}. Participants in the \textit{Throwing} and \textit{Detection} tasks were generally suboptimal in their perfomance. However, participants that completed the \textit{Reaching Task} were uniformly optimal. In this task, participants had to select a seat from one of three chairs in order to reach for bean bags arranged in a similar manner to that of the \textit{Throwing Task}. The same logic still applied; when the bean bags were close, one could choose a central location and be successful, however when they were far apart, it made more sense to pick one of the side chairs. The biggest difference here is that for the furthest separations, it would have been impossible for the participants to reach should they have selected the central chair.

@@

\subsection*{Individual Differences}
\addcontentsline{toc}{subsection}{Individual Differences}
\paragraph{} Finally, in this experiment a similar result of most participants being suboptimal was replicated. Yet, again there were a minority of participants that were close to performing optimally. This result is seen in other tasks that may be considered more complex \citep{Zhang2012handeye}. In a study by \cite{Zhang2012handeye}, participants had to search through two clusters of quite complicated objects and reach for the target item. The clusters differed in terms of size with two objects being in one and four in the other. Under the time constraints placed on their participants, the best strategy would be to look at the smaller cluster (as this is the easiest to dismiss) but simultaneously reach for the larger cluster as this has the higher chance of containting the target. Most participants did not appear to show any real preference for examining either cluster first. However, two participants showed a very clear preference by searching the smaller cluster first 90\% of the time. Even in this slightly more complex task, there were still participants that were able to approximate the optimal solution. This pattern is also seen in a lot of the biases and heuristics literature in which most participants fall for certain biases (such as the \textit{Gambler's Fallacy}), but some are able to overcome this and provide less biased response \cite{stanovich2008relative}

@@

\paragraph{} It is not immediately clear what may have allowed participants in the current study and \cite{clarke2015failure} to be able to closely approximate the optimal strategy. It would be interesting to examine whether people that are able to avoid falling for various biases and hueristics tasks would be more likely to perform optimally in this task. As such, future research should aim to include some other short tasks such as those discussed in \cite{Toplak2011}.

>>>>

\begin{titlepage}
	\centering
	%\includegraphics[width = number\textwidth]{image title}\par\vspace{1cm}}
	%this could be used to add the Aberdeen logo?
	%{\scshape\Large The University of Aberdeen \par}
	%\vspace{1cm}
	{\huge\bfseries Asymmetry and the Absence of Patterns Do Not Encourage Optimal Decisions.\par}
	\vspace{1cm}
	Warren \textsc{James}, \par
	Dr.~Amelia \textsc{Hunt},\par
	and\par
	Dr.~Alasdair \textsc{Clarke}
	\vfill
\end{titlepage}

@@

\paragraph{} Some theories assume that people generally aim to make decisions that offer the greatest expected utility \citep{mongin1997expected}. However, problems can become intractable as the number of possible outcomes to compare grows \citep[see ][ for a discussion of this]{BOSSAERTS2017917}. Therefore, when thinking of optimal decisions, one must take into account the limitations of the individual. This is termed Bounded Rationality \citep{simon1990invariants} and posits that people do make optimal decisions given some limitations.

@@

\paragraph{} This possibility was investigated in \cite{James2017} using the \textit{Throwing Task} with the added measure of what participants understood their ability to be.  The results of this experiment suggested that all participants had a very clear understanding of their own ability. Prompting participants to think about their accuracy on each trial, however, did not appear to make participants better able to solve the problem presented to them. The results of \cite{James2017} appear to suggest either a failing of \textit{Bounded Rationality} in that participants were not considering/using knowledge of their ability to accurately throw bean bags appropriately, or that they were simply more focused on other aspects of the task that may have caused them to ignore this information. In the four studies presented here, the aim was to investigate what aspects of the task may have interfered with the participants' ability to figure out the optimal strategy.

@@

\subsection*{Probability Matching}
\addcontentsline{toc}{subsection}{Probability Matching}
%This is just a temporary intro to this section that can be edited at any point depening on where it is positioned in the final version
\paragraph{} The first of these factors to be investigated is that of \textit{Probability Matching}. This is often regarded as a suboptimal behaviour as it does not offer the greatest rate of success \citep{Koehler2010}. An example of this would be if one was tasked with selecting between two options several times in a row. If option A would reward you 80\% of the time, and option B only 20\% of the time. The best course of action is to pick option A every time as this would result in an average success rate of 80\%. Whereas trying to match the probabilities by selecting each option in proportion to its likelihood of success would only yield an average success rate of 68\%.

@@

\paragraph{} As \cite{wolford2004searching} suggest, this search for a pattern may hinder performance in tasks in which there is no true pattern to find. In the context of \cite{clarke2015failure}, this may have interfered with participants using information about their own ability to make decisions. Instead, they may have been attempting to figure out any patterns that they believed may have been present. %In study 2 of this paper, a bias for one side was included to examine whether participants would begin to make use of this information. The hypothesis was that in a context where each option is equally likely, we should replicate the results of \cite{clarke2015failure}, however, once a bias is added, participants would be more likely to prioritise this target and begin to opt for choosing to attempt one task rather than try to achieve both.

@@

\begin{figure}
	\centering
	\captionsetup{justification=centering}
	\subfloat{\includegraphics[height = 10cm, width = 15cm]{Figures/Experiment_4_prob/exp_vs_opt_bias_lines}}\quad
	\subfloat{\includegraphics[height=10cm,width=15cm]{Figures/Experiment_4_prob/exp_vs_opt_rand_lines}}
	\caption{The different lines represent the predicted accuracy given the participant had employed either the optimal or centre strategy, and their expected accuracy given the fixation locations the participant made in the experiment.}
	\label{fig:Session2-prob-accresults}
\end{figure}

@@

\paragraph{} The results of both \cite{CHAPMAN2010168} and \cite{Hudson2007probmove} suggest that people were trying to give themselves a more evenly distributed chance of success. This suggests that participants preferred more equal odds of success to having a high chance of success for some (if not 100\%) and the other having a much lower chance of success (if not $\approx$0\%). Also, in \cite{Hudson2007probmove}, we can see how participants demonstrated a reluctance to move entirely towards the most probable location and instead favoured points that allowed for a small chance of success should the unlikely happen.

@@

\paragraph{} To confirm this, a General Linear Mixed Effects model with a binomial link was used. For the model, the small hoop being on the left or right was used a predictor for whether the participant stood either on the left or right of centre. The results of this model were significant suggesting that participants were more likely to stand towards the small hoop than the large one (the model specification can be seen below). This suggests that participants were somewhat aware that their chances would improve slightly should they have stood slightly closer to the smaller hoop. This is in line with the data presented by \cite{CHAPMAN2010168} in that the participants were positioning themselves in such a way that may have given them a more equal chance of success should either target be the target for that trial.

@@

\paragraph{} Upon inspecting Figure \ref{fig:Session2-Hoopsizes-Accuracy}, there is little noticeable difference between the expected accuracy should the participant have decided to stand equidistant from each hoop or in the position that offered the participant more equal chance of success. Additionally, by creating a more tangible situation in which there is a clear reason to prioritise one target over the other, participants generally still do not appear to reach the optimal solution. Participants 10, 11, and 12 are close to achieving optimal accuracy for both the closest and furthest hoops, however, as can be seen in Figure \ref{fig:Session2-Hoopsizes-Accuracy}, they still fall short of reaching optimal accuracy.

@@

\paragraph{} In \textit{Experiment 2}, the intention was to provide participants with a more tangible experience of one of the potential targets being more rewarding than the other. Similar to the results of \cite{CHAPMAN2010168} and \cite{Hudson2007probmove}, the participants in this experiment appeared to demonstrate a general tendency to move towards a position that would offer them a more equal chance of success. This is demonstrated by participants on average standing towards the smaller hoops in this task. However, this change to the paradigm still did not facilitate a better understanding of the task that would lead to an optimal strategy being implemented.

@@

\paragraph{} From visually inspecting Figure \ref{fig:Session2-TwoThrows}, one can see that for the most part, the number of throws had no real effect on where participants chose to stand. The only participant that appears to show some difference is participant 15 and this is in the opposite direction to what would have been expected should removing any reason to search for patterns had impeded participants' ability to figure out the optimal strategy.

@@

\paragraph{} Inspecting Figure \ref{fig:Session2-TwoThrows-Accuracy} demonstrates that most participants achieved an accuracy that would be expected had they followed the Centre strategy. The one exception to this is participant 13 who appears to achieve an accuracy close to the optimal strategy. By looking at the participant's standing positions in \ref{fig:Session2-TwoThrows}, this would make sense as they appear to switch at an appropriate point given their own ability to perform in this task. Although they did appear to stand outside the range for some distances, it appears that they were more likely to stand in a central position for the smallest distances, and towards one of the sides for the larger distances.

@@

\paragraph{} As with any decision to be made, having appropriate incentives for success can be important. \cite{phillips1966conservatism} investigated this idea by tasking participants with estimating whether a bag they had been handed contained predominantly red or blue chips. They were told there were 10 bags in total with $X$ containing predominantly red chips and $10 - X$ containing predominantly blue chips. They were then told that the bags that contained mainly red chips either contained 70\% red chips and 30\% blue, or 60\% red and 40\% blue with the inverse of these being true for the predominantly blue bags. They were then presented with 20 chips from the selected bag and were asked to give an estimate of how likely the bag the chips were drawn from was a majority red or majority blue bag. What they found was that participants estimates were fairly conservative when compared to what would be expected via Bayesian inference. They questioned whether this could be due to a lack of incentive to perform this task more effortfully.

@@

\paragraph{} Another example of a payoff structure altering the behaviour of participants can be seen in \cite{Goodnow1955} in which participants that were rewarded for performance were more likely to employ a more optimal strategy. They tasked participants with making judgements of which event would occur on each trial. The likelihood of each event occurring was set in one of three ways; being equally likely, a 70\% bias in favour of one event, or a 90\% bias in favour of one event occurring. Half the participants were told that the task was one of learning and that they were to uncover some underlying principle, whereas the other half were told that the task was one of gambling in which they were to place a bet on which event was likely to occur on each trial. They found that participants in the gamble condition when there was a 70\% bias were more likely to opt for a \textit{maximising} strategy than those in the problem solving condition. This was also true for the 90\% bias condition, but the effect appeared less pronounced.

\paragraph{} Although these studies do suggest that a financial incentive may have pushed some participants to perform the task in a more optimal way, it did not cause them to perform the tasks perfectly optimally. In a review by \cite{Camerer1999}, it is argued that a financial incentive is not entirely enough to remove all irrational behaviours. This can clearly be seen in \cite{morvan2012human} in which participants received a small sum of money for every successful trial. Despite this financial incentive, participants did not appear to behave any differently to those in \cite{clarke2015failure} who did not pay their participants any amount for successful trials.

@@

\subsection*{Preface}
\addcontentsline{toc}{subsection}{Preface}
\paragraph{} As mentioned before, in \textit{Experiment 1}, participants were tasked with tracking a fairly abstract concept of probability. They would have needed to recognise that the location with the highest likelihood of containing the target would reward them with the greatest rate of return in the long term. As such, it is possible that participants did not see the more likely option as being more valuable, but instead would try to make use of this information in another way. \cite{Goodnow1955} demonstrated that when participants were offered a financial incentive for success, they were more likely to make use of a maximising strategy over the less optimal alternative of probability matching. In \textit{Experiment 4}, we attempted to investigate this by introducing a very clear, external reward for successful performance in the task.

@@

\subsubsection*{Procedure} 
\paragraph{} Participants signed a consent which contained details about the reward schedule and how much they could expect to earn on average. All participants were given £4 as a baseline and were told that they could expect to earn an additional amount ranging from £0 to £4.80 depending on their performance. They were also told that we expected them to earn between £1.50 and £2.50 on average.

@@

\paragraph{} There were two main changes to the paradigm for this experiment. Firstly, instead of calculating 3 distances, 4 were calculated. Now, the distances at which participants were 90\%, 75\%, 25\%, and 10\% accurate were used. Additionally, participants were now told they had 50p to split between the two target items in one of two ways. They could either split it equally across both potential targets (25p/25p) or make it an 80/20 split (40p/10p). Participants were asked how they would like to split the money before they made a choice about where to stand. If they opted to make an unequal split, they were asked which hoop they would like to be worth 40p and which 10p. Participants were informed that the target hoop had been predetermined so that each hoop was equally likely to be the target on each trial and that there was no pattern. It was reaffirmed that any money they earned by successfully throwing the bean bag into the target hoop would be given to them upon completing the experiment. Participants would then pick a place to stand, at which point they would be told which hoop was the target for that trial and their standing position was recorded covertly.

@@

\paragraph{} As can be seen in Figure \ref{fig:DecisionPhase_Reward}, participants generally tended towards splitting the monetary value in an Equal fashion. Only four participants opted for an Unequal split most of them time, but no participants followed the truly optimal rule of always splitting the value Unequally which would have given participants a larger rate of return.

@@

\paragraph{} However, these two experiments do offer some insight into information people may be attempting to make use of when performing these sorts of tasks. For example, in \textit{Experiment 1}, participants generally were more likely to prioritise one side over the other when there was a reason to do so. Although they did not quite make use of this information in an optimal way (i.e. by exclusively fixating the more likely box) as would be expected \citep{koehler2014probability}, there was a difference when compared to a situation in which each option was equally likely. This adds further support to the notion that people are sensitive to this information and will make use of it when making decisions \citep{wolford2004searching,yellott1969probability}. Due to this, it is possible that participants were in fact making an attempt to maximise their rate of success, but were doing so using a suboptimal strategy \citep{Gao2015}.

@@

\subsection*{Confidence}
\addcontentsline{toc}{subsection}{Confidence}
\paragraph{} In general, participants still made suboptimal decisions across all tasks. This raises the question of whether participants are making their decisions about where to stand with confidence, or whether they recognise when they are doing something that might not be "correct". \cite{SZOLLOSI20171} presented people with a series of questions with the three items from the Cognitive Reflection Task \citep[CRT: ][]{Frederick2005CRT}. These items are designed so that an intuitive, but incorrect, answer will spring to mind. An example of one of these items the bat and ball problem which goes as follows; \textit{"a bat and a ball cost \pounds1.10. The bat costs \pounds1.00 more than the ball. How much does the ball cost?"} The correct answer is 5p, yet many people often state the ball is worth 10p causing the total to be \pounds1.20 \citep{Frederick2005CRT}. In the study by \cite{SZOLLOSI20171}, they gave people many problems like these and also asked participants to give a rating of how confident they were that they had given the correct answer. When tasked with answering the items from the CRT and giving the wrong answer, participants tended to be less confident that they had given the right answer. Additionally, their participants indicated that they had also spent less time trying to figure out the answer to questions they were less confident in. They argued that these coupled together suggest that people recognised that the task was "too difficult" and offered the solution that first came to mind.

\paragraph{} The idea that people may simply give up and offer the first solution that comes to mind is similar to the idea of "satisficing" \citep{simon1990invariants}. This is when someone finds a task too difficult and as such attempts to solve the problem using little effort such as using a strategy that has worked before in other contexts. It's possible that once participants find the tasks in this paper to be too difficult, they gave up and continued to behave in the same way as before. One way to investigate this would be to use a similar paradigm to that employed by \cite{Kiani759}. In their study, they presented monkeys with a large number of moving dots on a screen and they were to report the "global direction" of the dots (i.e. were they mainly moving to the left or the right). For each correct answer, they received an amount of juice In some cases this would be easy to estimate as a large proportion of the dots would be moving as a group. However, in some cases, only a small proportion would be moving in one direction with the rest moving at random. In these situations it became more difficult for them to discern the "global direction" of the dots. On random trials they were offered a third option that would offer a certain reward, but this was worth less than if they gave the correct answer. What they found was that the monkeys would use this option when the task was more difficult.

\paragraph{} This idea of confidence could easily be incorporated into the tasks used in this paper in order to investigate whether people may simply be satisficing rather than trying to figure out a solution. Much like in \cite{Kiani759}, a third option could be introduced on random trials that would give a small but certain reward. If participants are able to recognise their own ability to perform but cannot figure out the solution to the task, then what would be observed is that participants would continue to stand more towards the centre, but only opt for the 3rd, lesser value but certain option, when the task became harder. 
%This would enatil that participants would need to have some sort of performance related reward, and although this does not seem to make a difference when comparing the performance of participants with reward \citep{morvan2012human} and without \citep{clarke2015failure}, it does allow for the hypothesis that participants are simply satisfying to be investigated.
%Satisfising is argued to be due to people reaching a certain success threshold and the ceasing to search for alternative strategies that may improve their performance. As such, it would be possible to alter the amount of reward participants would receive if they selected the 3rd option. With a setup like this, it would be possible to investigate whether a lack of confidence in one's capacity to solve this problem results in settling for a relatively low success rate.

%This paragraph is weak... maybe rephrase it a bit or develop the idea a bit more?
%\paragraph{} Additionally, adding a financial incentive for success allows for other potential factors to be investigated. Although in \cite{James2017}, participants were able to give accuracte measures of their own ability, this does not necessarily mean that they would incorporate this information into their decision making. \cite{Goodnow1955} argued that in the context of problem solving, people are more likely to probability match, within a gambling context, people tend to maximise. Within the context of this study, the paradigm could be altered so that participants would have sum of money they would split between each target. For example, they could split the amount equally between each target. If the they were then successful for the selected target, they would receive the amount they had placed on that target. By doing this, participants would now have more reason to consider their odds of success should they desire to gain the largest financial reward. This would make it so that not only would participants be considering their own ability to perform, but it may push them to incorporate this information more effectively into their decision making, rather than possibly treating it as an extra task to be performed concurrently.
%
\subsection*{Certainty}
\addcontentsline{toc}{subsection}{Certainty}
%\paragraph{} Adding in a gambling element may lead participants to consider aspects of the problem that they may not have considered without this extra factor. 
\paragraph{} None of these experiments are able to investigate an intriguing contradiction in \cite{clarke2015failure}. Participants in the \textit{Throwing} and \textit{Detection} tasks were generally suboptimal in their performance. However, participants that completed the \textit{Reaching Task} were uniformly optimal. In this task, participants had to select a seat from one of three chairs in order to reach for bean bags arranged in a similar manner to that of the \textit{Throwing Task}. The same logic still applied; when the bean bags were close, one could choose a central location and be successful, however when they were far apart, it made more sense to pick one of the side chairs. The biggest difference here is that for the furthest separations, it would have been impossible for the participants to reach should they have selected the central chair.

@@

\subsection*{Individual Differences}
\addcontentsline{toc}{subsection}{Individual Differences}
\paragraph{} Finally, in this experiment a similar result of most participants being suboptimal was replicated. Yet, again there were a minority of participants that were close to performing optimally. This result is seen in other tasks that may be considered more complex \citep{Zhang2012handeye}. In a study by \cite{Zhang2012handeye}, participants had to search through two clusters of quite complicated objects and reach for the target item. The clusters differed in terms of size with two objects being in one and four in the other. Under the time constraints placed on their participants, the best strategy would be to look at the smaller cluster (as this is the easiest to dismiss) but simultaneously reach for the larger cluster as this has the higher chance of containing the target. Most participants did not appear to show any real preference for examining either cluster first. However, two participants showed a very clear preference by searching the smaller cluster first 90\% of the time. Even in this slightly more complex task, there were still participants that were able to approximate the optimal solution. This pattern is also seen in a lot of the biases and heuristics literature in which most participants fall for certain biases (such as the \textit{Gambler's Fallacy}), but some are able to overcome this and provide less biased response \cite{stanovich2008relative}

@@

\paragraph{} It is not immediately clear what may have allowed participants in the current study and \cite{clarke2015failure} to be able to closely approximate the optimal strategy. It would be interesting to examine whether people that are able to avoid falling for various biases and heuristics tasks would be more likely to perform optimally in this task. As such, future research should aim to include some other short tasks such as those discussed in \cite{Toplak2011}.
